To Do List

### 2019-06-01 Papers.Rmd
Add DeepMILO paper

>>>>

- Trieu, Tuan, and Ekta Khurana. “A Deep Learning Approach to Predict the Impact of Non-Coding Sequence Variants on 3D Chromatin Structure.” BioRxiv, January 1, 2019, 516849. https://doi.org/10.1101/516849. - DeepMILO - learn TAD boundaries and predict the effect of genomic variants on them. Convolutional and recurrent neural networks (CNN, RNN), distinguishes CTCF and cohesin vs. CTCF only. Trained on experimental CTCF peaks overlapping RAD21 peaks (Gm12878). CTCF orientation is important, Figure 2a, detected by FIMO tool. https://github.com/tuantrieu/DeepMILO
